### 2010-11-27 Text/paper.tex
Minor changes with Latex file.

\documentclass{article}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
\begin{document}
\begin{abstract}
Recently we investigated the applicability and parameters choice for the two-dimensional case
Bretherton problem. This paper is focused on the three-dimensional case to validate the continuous
interface methods to simulate phenomena happening in the Bretherton/Taylor flow for rectangular
and square capillaries. 
\end{abstract}
\section{Introduction}
While for two-dimensional Bretherton flow the results are usually limited to the circular shape and
only some of them are for the plane-symmetric case \cite{giavedoni-numerical,heil-planar},
vast number of experimental results and simulations are available for the three-dimensional case.
It was found that the for rectangular and/or square shaped capillaries there is a transition for
certain capillary number, where the flow changes from the non axi symmetric to axis symmetric case.
The number is indicated in a number of works of as $Ca=0.04$ \cite{cerro-bubble-train}, $Ca=0.1$
\cite{cerro-space}, $Ca=0.033$ and for $Ca>4$ \cite{heil-threedim} measured at 11 half-widths behind
the finger tip.

@@

\section{Non-axisymmetric case}
That could be fucking difficult. For example according to \cite{heil-threed} for the capillary
number $Ca=0.01$, the radiuses converge as $r_h=0.99$ and $r_d=1.1$. Therefore one needs to resolve
as the $0.5\%$ of whole channel width to see the difference. That certainly implies so large grid
that can kill the simulation at least $200x200x3000$. However, we can refer to artificially made
interface as $1-2$ lattice Boltzmann units but keeping the capillary number as it is required. In
this case we can refer like we can't resolve the interface but we can certainly to attribute it to
the wall gradient as extreme case. The dimnesionalization case is therefore as follows:
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma},
\end{equation}
therefore let us pick up the same parameters as for the previous case and just change use the
pressure gradient reduced by $1000$ as $Ca=10$ and $Ca=0.01$ are different. 
Let us wait for simulation.

>>>>

\documentclass{article}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{color}
\begin{document}
\begin{abstract}
Recently we investigated the applicability and parameters choice for the two-dimensional case
Bretherton problem. This paper is focused on the three-dimensional case to validate the continuous
interface methods to simulate phenomena happening in the Bretherton/Taylor flow for rectangular
and square capillaries. 
\end{abstract}
\section{Introduction}
While for two-dimensional Bretherton flow the results are usually limited to the circular shape and
only some of them are for the plane-symmetric case \cite{giavedoni-numerical,heil-bretherton},
vast number of experimental results and simulations are available for the three-dimensional case.
It was found that the for rectangular and/or square shaped capillaries there is a transition for
certain capillary number, where the flow changes from the non axi symmetric to axis symmetric case.
The number is indicated in a number of works of as $Ca=0.04$ \cite{cerro-bubble-train}, $Ca=0.1$
\cite{cerro-space}, $Ca=0.033$ and for $Ca>4$ \cite{heil-threedim} measured at 11 half-widths behind
the finger tip.

@@

\section{Non-axisymmetric case}
That could be fucking difficult. For example according to \cite{heil-threedim} for the capillary
number $Ca=0.01$, the radiuses converge as $r_h=0.99$ and $r_d=1.1$. Therefore one needs to resolve
as the $0.5\%$ of whole channel width to see the difference. That certainly implies so large grid
that can kill the simulation at least $200x200x3000$. However, we can refer to artificially made
interface as $1-2$ lattice Boltzmann units but keeping the capillary number as it is required. In
this case we can refer like we can't resolve the interface but we can certainly to attribute it to
the wall gradient as extreme case. The dimnesionalization case is therefore as follows:
\begin{equation}
Ca=\frac{\mu_{liq} U_{bubble}}{\gamma},
\end{equation}
therefore let us pick up the same parameters as for the previous case and just change use the
pressure gradient reduced by $1000$ as $Ca=10$ and $Ca=0.01$ are different. 
Let us wait for simulation.
